Testable normative theories

### 2020-04-28 simple.tex
Cosmetic small impr
Strengthening (?) of Reinstatement in hope of replacing Bounded length (and because it is necessary for it to make sense anyway).

To lighten notations, $\ileadstost[i]$ will generally be denoted by $\ileadstost$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$. When the symbol $i$ is used in a formula without being bound, the binding $\forall i \in I$ is implied.

@@

\begin{definition}[Reinstatement]
	A theory satisfies \emph{reinstatement} iff $\forall \ar_1, \ar_3 \in \gargs[\phi], \ar_2 \in \allargs: [\ar_1 \ileadstoe \phi, (\ar_2, \ar_1) \ileadstoe ¬\phi, (\ar_3, \ar_2) \ileadstost \phi] ⇒ (\ar_1 + \ar_3, \ar_2) \ileadstost \phi$.
\end{definition}

>>>>

To lighten notations, $\ileadstost[i]$ will generally be denoted by $\ileadstost$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$. When the symbol $i$, $\ileadstost$ or $\gleadsto$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.

@@

\begin{definition}[Reinstatement]
	A theory satisfies \emph{reinstatement} iff $\forall \ar_1, \ar_3 \in \gargs[\phi], \ar_2 \in \allargs: [\ar_1 \ileadstoe \phi, (\ar_2, \ar_1) \ileadstoe ¬\phi, (\ar_3, \ar_2) \ileadstoe \phi] ⇒ (\ar_1 + \ar_3, \ar_2) \ileadstoe \phi \land [\forall \ar_4 \ibeatse \ar_1 + \ar_3: \ar_4 \ibeatse \ar_1 \lor \ar_4 \ibeatse \ar_3]$.
\end{definition}
